---
title: "p8105_hw1_xz3173"
author: "Xue Zhang"
date: "2023-09-19"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

Load the moderndive library.

```{r}
library(moderndive)
```

Load the early_january_weather dataset.

```{r}
data("early_january_weather")
```

Write a short description of the dataset using inline R code; accessing the dataset help file can be informative. 

This is a short description `early_january_weather` dataset. The summary of the dataset is `skimr::skim(early_january_weather)` here.This dataset has 15 variables, including `names(early_january_weather)`. The time of the recording of this dataset is on January, 2023 `early_january_weather %>% select(month)`, `early_january_weather %>% select(year)`. The duration of the dataset is 15 days `range(early_january_weather[["day"]])`. Everyday, the dataset is recording for 23 hours `range(early_january_weather[["hour"]])`. The range of the humidity is `range(early_january_weather[["humid"]])`. The mean of the humidity is `mean(early_january_weather[["humid"]])`.
The range of the temperature is `range(early_january_weather[["temp"]])`.
The mean of the temperature is `mean(early_january_weather[["temp"]])`.



Make a scatterlot.

```{r}
plot_df = tibble(
  x = early_january_weather[["time_hour"]],
  y = early_january_weather[["temp"]],
  color = early_january_weather[["humid"]]
)

ggplot(plot_df, aes(x = x, y = y, color = color)) + geom_point()
```


Describe patterns that are apparent in this plot.

**The temperature has been growing from January 1st to January 14th, which is below 50.Then, it is rapidly dropping down from January 14th to January 15th. The humidity has been change low-high-low between January 1st to 10th, which the color is often dark blue.The humidity has keep higher than 100 between January 11th and January 12th, which the color is light blue.**


Export scatterplot.

```{r}
ggsave("scatter_plot.pdf")
```



# Problem 2

Create a data frame.

```{r}
set.seed(1234)
my_dataset = tibble(
  random_sample = rnorm(10),
  vec_logical = c(random_sample > 0),
  vec_char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  vec_factor = factor(rep(c("Level 1", "Level 2", "Level 3"), length.out = 10))
)

my_dataset
```

Use pull to calculate mean.

```{r}
my_dataset %>%
  pull(random_sample)
mean(my_dataset[["random_sample"]])
```

```{r}
my_dataset %>%
  pull(vec_logical)
mean(my_dataset[["vec_logical"]])
```

```{r}
my_dataset %>%
  pull(vec_char)
mean(my_dataset[["vec_char"]])
```

```{r}
my_dataset %>%
  pull(vec_factor)
mean(my_dataset[["vec_factor"]])
```


**" Mean" works on Random_sample and vec_logical, do not work on vec_char and vec_factor. "Mean" use for numeric variables. Random_sample is classified as numeric. Vec_logical is classified as logical vector, which contains True/False values, as arithmetic.**



Write code chunk with as.numeric function.

```{r, eval = FALSE, message = FALSE}
mean(as.numeric(my_dataset[["random_sample"]]))
mean(as.numeric(my_dataset[["vec_logical"]]))
mean(as.numeric(my_dataset[["vec_char"]]))
mean(as.numeric(my_dataset[["vec_factor"]]))
```

**Numeric variables can calculate "mean". Logical variables, can be convert to numeric (0 or 1, True or False), and calculate "mean". Character variables such as "A","B", can not be converted to numeric values. Therefore, the results of mean comes back with NA values and warning message. Factor variables is a factor column with numeric levels, so the output comes back with values, which is not meaningful.**


