---
title: "p8105_hw1_xz3173"
author: "Xue Zhang"
date: "2023-09-19"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

Load the moderndive library.

```{r}
library(moderndive)
```

Load the early_january_weather dataset.

```{r}
data("early_january_weather")
```

Write a short description of the dataset using inline R code; accessing the dataset help file can be informative. 

* the variables in this dataset, including names/values of important variables


```{r}
names(early_january_weather)

```

```{r}
early_january_weather

```

```{r}
head(early_january_weather)
```


```{r}
tail(early_january_weather)
```


```{r}
skimr::skim(early_january_weather)
```

* the size of the dataset
nrow = number of rows in the dataset
ncol = number of columns in the dataset

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```

* the mean temperature

```{r}
mean_temp = early_january_weather$temp
mean(mean_temp)
```


Make a scatterlot of temp (y) vs time_hour (x); color points using the humid variable (adding color = ...) inside of aes in your ggplot code should help). Describe patterns that are apparent in this plot.

```{r}
plot_df = tibble(
  x = early_january_weather$time_hour,
  y = early_january_weather$temp
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

Export your scatterplot to your project directory using ggsave.


```{r}
ggsave("scatter_plot.pdf")
```

# Problem 2
